Vocabulary

### 2022-01-13 docs/02_vocabulary.Rmd
Add both models

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = TRUE,
	warning = TRUE, 
	cache.extra = knitr::rand_seed,
	out.width = "80%",
	results = "asis",
	dpi = 300,
	dev.args = list(png = list(type = "cairo"))
)
options(
	knitr.kable.NA = '-',
	knitr.duplicate.label = "allow",
	ggplot2.discrete.fill = ggsci::pal_tron("legacy")(7),
	ggplot2.discrete.colour = ggsci::pal_tron("legacy")(7)
)

@@

participants <- participants %>% 
	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
	drop_na(participant) %>% 
	left_join(vocabulary) %>% 
	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1])
```

@@

# vocabulary
participants %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot() +
	facet_grid(location~age_group) +
	# geom_violin(
	# 	position = position_dodge(width = 0.75),
	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
	# ) + 
	geom_hline(yintercept = 0.5, colour = "white") +
	geom_point(
		aes(lp, vocab_size_l1),
		shape = 1, colour = "white", size = 1, stroke = 1,
		position = position_jitter(width = 0.1, seed = 888)
	) +
	geom_boxplot(
		aes(lp, vocab_size_l1, fill = lp),
		width = 0.25, outlier.colour = NA,
		position = position_dodge(width = 0.75), size = 1
	) +
	geom_text(
		data = sample_size,
		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
		colour = "white", fill = "white", show.legend = FALSE
	) +
	labs(y = "Receptive vocabulary (L1)", colour = "Group", fill = "Group") +
	scale_y_continuous(limits = c(0, 1), labels = percent) +
	theme(
		legend.title = element_blank(),
		legend.position = "none",
		panel.grid.major.y = element_blank(),
		axis.title.x = element_blank(),
		axis.text = element_text(size = 9)
	)

@@

```{r vocabulary_total, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
sample_size <- participants %>% 
	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
	count(age_group, location)

# vocabulary
participants %>% 
	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot() +
	facet_grid(location~age_group) +
	# geom_violin(
	# 	position = position_dodge(width = 0.75),
	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
	# ) + 
	geom_hline(yintercept = 0.5, colour = "grey") +
	geom_point(
		aes(lp, vocab_size_total),
		shape = 1, colour = "white", size = 1, stroke = 1,
		position = position_jitter(width = 0.1, seed = 888)
	) +
	geom_boxplot(
		aes(lp, vocab_size_total, colour = lp, fill = lp),
		width = 0.25, fill = "#0D1117", outlier.colour = NA,
		position = position_dodge(width = 0.75), size = 1
	) +
	geom_text(
		data = sample_size,
		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
		colour = "white", fill = "white", show.legend = FALSE
	) +
	labs(y = "Receptive vocabulary (L1+L2)", colour = "Group", fill = "Group") +
	scale_y_continuous(limits = c(0, 1), labels = percent) +
	theme(
		legend.title = element_blank(),
		legend.position = "none",
		panel.grid.major.x = element_blank(),
		axis.title.x = element_blank(),
		axis.text = element_text(size = 9),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
	)

@@

```{r vocabulary_conceptual, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
sample_size <- participants %>% 
	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
	count(age_group, location)

# vocabulary
participants %>% 
	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot() +
	facet_grid(location~age_group) +
	# geom_violin(
	# 	position = position_dodge(width = 0.75),
	# 	aes(lp, vocab_size_l1, colour = lp, fill = lp)
	# ) + 
	geom_hline(yintercept = 0.5, colour = "grey") +
	geom_point(
		aes(lp, vocab_size_conceptual),
		shape = 1, colour = "white", size = 1, stroke = 1,
		position = position_jitter(width = 0.1, seed = 888)
	) +
	geom_boxplot(
		aes(lp, vocab_size_conceptual, colour = lp, fill = lp),
		width = 0.25, fill = "#0D1117", outlier.colour = NA,
		position = position_dodge(width = 0.75), size = 1
	) +
	geom_text(
		data = sample_size,
		aes(x = 1.5, y = 0.95, label = paste0("n = ", n)),
		colour = "white", fill = "white", show.legend = FALSE
	) +
	labs(y = "Receptive vocabulary (coneptual)", colour = "Group", fill = "Group") +
	scale_y_continuous(limits = c(0, 1), labels = percent) +
	theme(
		legend.title = element_blank(),
		legend.position = "none",
		axis.title.x = element_blank(),
		axis.text = element_text(size = 9),
		panel.grid.major.x = element_blank()
	)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = TRUE,
	warning = TRUE, 
	cache.extra = knitr::rand_seed,
	out.width = "80%",
	results = "asis",
	dpi = 300,
	dev.args = list(png = list(type = "cairo"))
)
options(
	knitr.kable.NA = '-',
	knitr.duplicate.label = "allow",
	ggplot2.discrete.fill = ggsci::pal_futurama()(7),
	ggplot2.discrete.slab_color = ggsci::pal_futurama()(7),
	ggplot2.discrete.colour = ggsci::pal_futurama()(7)
)

@@

participants <- participants %>% 
	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
	drop_na(participant) %>% 
	left_join(vocabulary) %>% 
	mutate(vocab_size_l1_center = scale(vocab_size_l1)[,1]) %>% 
	filter(location=="Barcelona")
```

@@

sample_size_lp <- participants %>% 
	filter(valid_participant, !is.na(vocab_size_l1)) %>% 
	count(age_group, lp, location) %>% 
	mutate(
		age_group = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		)
	)

# vocabulary
participants %>% 
	mutate(
		age_group = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		)
	) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot() +
	facet_wrap(~age_group, scales = "free_x") +
	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
	stat_pointinterval(
		aes(lp, vocab_size_l1, group = lp),
		position = position_nudge(x = 0.2),
		.width = c(0.95, 0.89, 0.50),
		point_size = 3
	) +
	geom_point(
		aes(lp, vocab_size_l1, color = lp),
		shape = 1, size = 3, stroke = 1.5, alpha = 0.75,
		position = position_jitter(width = 0.1, seed = 888)
	) +
	geom_text(
		data = sample_size_lp,
		aes(x = 1.5, y = 0, label = paste0("N = ", n), group = lp),
		show.legend = FALSE, position = position_dodge(width = 2)
	) +
	labs(
		y = "Receptive vocabulary (L1)", colour = "Group", fill = "Group",
		title = "Total vocabulary size",
		subtitle = "Percentage of words in L1+L2 reported to be understood from the vocabulary checklist"
	) +
	guides(colour = "none") +
	scale_color_manual(aesthetics = "slab_color", values = pal_futurama()(2)) +
	scale_y_continuous(limits = c(0, 1), labels = percent) +
	theme(
		legend.title = element_blank(),
		legend.position = "top",
		panel.grid.major.x = element_blank(),
		axis.title.x = element_blank(),
		axis.text = element_text(size = 9)
	)

@@

```{r vocabulary_total, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
sample_size <- participants %>% 
	filter(valid_participant, !is.na(vocab_size_total)) %>% 
	count(age_group, location)

sample_size_lp <- participants %>% 
	filter(valid_participant, !is.na(vocab_size_total)) %>% 
	count(age_group, lp, location) %>% 
	mutate(
		age_group = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		)
	)

# vocabulary
participants %>% 
	mutate(
		age_group = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		)
	) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot() +
	facet_wrap(~age_group, scales = "free_x") +
	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
	stat_pointinterval(
		aes(lp, vocab_size_total, group = lp),
		position = position_nudge(x = 0.2),
		.width = c(0.95, 0.89, 0.50),
		point_size = 3
	) +
	geom_point(
		aes(lp, vocab_size_total, color = lp),
		shape = 1, size = 3, stroke = 1.5, alpha = 0.75,
		position = position_jitter(width = 0.1, seed = 888)
	) +
	geom_text(
		data = sample_size_lp,
		aes(x = 1.5, y = 0, label = paste0("N = ", n), group = lp),
		show.legend = FALSE, position = position_dodge(width = 2)
	) +
	labs(
		y = "Receptive vocabulary (L1)", colour = "Group", fill = "Group",
		title = "L1 vocabulary size",
		subtitle = "Percentage of words in L1 reported to be understood from the vocabulary checklist"
	) +
	guides(colour = "none") +
	scale_color_manual(aesthetics = "slab_color", values = pal_futurama()(2)) +
	scale_y_continuous(limits = c(0, 1), labels = percent) +
	theme(
		legend.title = element_blank(),
		legend.position = "top",
		panel.grid.major.x = element_blank(),
		axis.title.x = element_blank(),
		axis.text = element_text(size = 9)
	)

@@

```{r vocabulary_conceptual, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
sample_size <- participants %>% 
	filter(valid_participant, !is.na(vocab_size_conceptual)) %>% 
	count(age_group, location)

sample_size_lp <- participants %>% 
	filter(valid_participant, !is.na(vocab_size_total)) %>% 
	count(age_group, lp, location) %>% 
	mutate(
		age_group = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		)
	)

# vocabulary
participants %>% 
	mutate(
		age_group = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		)
	) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot() +
	facet_wrap(~age_group, scales = "free_x") +
	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
	stat_pointinterval(
		aes(lp, vocab_size_conceptual, group = lp),
		position = position_nudge(x = 0.2),
		.width = c(0.95, 0.89, 0.50),
		point_size = 3
	) +
	geom_point(
		aes(lp, vocab_size_conceptual, color = lp),
		shape = 1, size = 3, stroke = 1.5, alpha = 0.75,
		position = position_jitter(width = 0.1, seed = 888)
	) +
	geom_text(
		data = sample_size_lp,
		aes(x = 1.5, y = 0, label = paste0("N = ", n), group = lp),
		show.legend = FALSE, position = position_dodge(width = 2)
	) +
	labs(
		y = "Receptive vocabulary (L1)", colour = "Group", fill = "Group",
		title = "Conceptual vocabulary size",
		subtitle = "Percentage of lexicalised concepts reported to be understood from the vocabulary checklist"
	) +
	guides(colour = "none") +
	scale_color_manual(aesthetics = "slab_color", values = pal_futurama()(2)) +
	scale_y_continuous(limits = c(0, 1), labels = percent) +
	theme(
		legend.title = element_blank(),
		legend.position = "top",
		panel.grid.major.x = element_blank(),
		axis.title.x = element_blank(),
		axis.text = element_text(size = 9)
	)
